Opening Restaurants During COVID-19 Can Prove Beneficial for Restaurant Revenue in the GTA

### 2021-02-27 outputs/Paper.Rmd
update!
uptade

thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
bibliography: references.bib
---

@@

# Data 
In this report, we use the R statistical programming language [@citeR]. To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1], "ggthemes" is used to change the diagram theme [@themes].
The survey conducted by Petit Poll collects the following data:

@@

setwd("~/Downloads/Git/groupproject-")

# read raw dataset from scripts, need to run survey_response _simulation first.
simulated_data<- read_csv("inputs/simulated_data.csv")

>>>>

thanks: 'Code and data are available at: https://github.com/yangg1224/GTA_Restaurant-.git'
bibliography: references.bib
---

@@

# Data 
In this report, we use the R statistical programming language [@citeR]. To be specific, we use the `tidyvers` package to process data [@citetidyverse], `kableExtra` package to generate tables [@citekableExtra],  `ggplot2` is used to draw diagrams [@gg1], `ggthemes` is used to change the diagram theme [@themes].
The survey conducted by Petit Poll collects the following data:

@@

library(here)

# read raw dataset from scripts, need to run survey_response _simulation first.
simulated_data<- read_csv(here::here("inputs/simulated_data.csv"))
